---
title: "1-Reading in Data"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Overall Structure of the code
### Source
In this file, we read in the data from the [LAPOP Datasets](http://datasets.americasbarometer.org/database/index.php). In order to do this, you need to download them to your machine and place them in this file.

### Workflow
Suggested order to follow:
1. Reading in Data
2. Categories and Questions
3. Adding Wave Column
4. Creating Unique ID
5. Lengthening and Joining
6. Finding Common Questions
7. Widening for Tableau Public
8. Writing .csv

### Factored vs. Unfactored
The data in the Stata files are factored, meaning that a yes or no question would be entered in as 0 and 1. These numbers are then assigned labels as such: 0 - "yes" and 1 - "no", and we refer to data frames where the labels are visible in the observations as *factored*. When data frames use only the numbered observations, we refer to this as *unfactored*.

We use both versions of the data frames for ease of use in Tableau Public. Unfactored data frames allow us to perform calculations in Tableau Public later on, and the factored data frames provide reader-friendly text to the graphics.

## Libraries
These packages contain the functions that are necessary to run the code below. These can be installed using `install.packages()`, and then you should run the code chunk below so they are ready to be used.
```{r Import ibraries, message=FALSE}
library(labelled)
library(sjmisc)
library(tidyverse)
library(assertr)
library(haven)
library(varhandle)
library(janitor)
library(rlang)
library(readxl)
library(fs)

```



# Reading in merged country files
This is where we read in all the factored data. You should use the *most recent* merged country files for this section. The factored and unfactored file names are the same.

If you want to change the files that are being read in, you can either make a new code chunk or replace the current file names. If you do this, you have to make sure there is an unfactored version of the file as well.



## Creating unfactored dataframes using `read_dta`
This is where we read in the unfactored data.
```{r Create unfactored df}
argentina_unfactor <- read_dta("data/merged_argentina_2008_2014.zip")

belize_unfactor <- read_dta("data/merged_belize_2008_2014.dta")

bolivia_unfactor <- read_dta("data/merged_bolivia_2004_2014.zip")

brazil_unfactor <- read_dta("data/merged_brazil_2007_2014.zip")

canada_unfactor <- read_dta("data/merged_canada_2006_2017.dta") %>% 
  #Fixing inconsistency
  rename(idnum_14 = idnum_1416)

chile_unfactor <- read_dta("data/merged_chile_2006_2014.zip")

colombia_unfactor <- read_dta("data/merged_colombia_2004_2014.zip")

costa_unfactor <- read_dta("data/merged_costa_rica_2004_2014.zip")

ecuador_unfactor <- read_dta("data/merged_ecuador_2004_2014.zip")

elsalvador_unfactor <- read_dta("data/merged_el_salvador_2004_2014.zip")

guatemala_unfactor <- read_dta("data/merged_guatemala_2004_2014.zip")

guyana_unfactor <- read_dta("data/merged_guyana_2006_2014.dta")

#haiti_unfactor <- read_dta("data/merged_haiti_2006_2014.zip")

honduras_unfactor <- read_dta("data/merged_honduras_2004_2014.zip")

jamaica_unfactor <- read_dta("data/merged_jamaica_2006_2017.dta") %>% 
  #Fixing inconsistency
  rename(idnum_14 = idnum_1416)

mexico_unfactor <- read_dta("data/merged_mexico_2004_2014.zip")

nicaragua_unfactor <- read_dta("data/merged_nicaragua_2004_2014.zip")

panama_unfactor <- read_dta("data/merged_panama_2004_2014.zip")

paraguay_unfactor <- read_dta("data/merged_paraguay_2006_2014.zip")

peru_unfactor <- read_dta("data/merged_peru_2006_2014.zip")

suriname_unfactor <- read_dta("data/merged_suriname_2010_2014.zip")

usa_unfactor <- read_dta("data/merged_united_states_2006_2017.dta") %>% 
  #Fixing inconsistency
  rename(idnum_14 = idnum_1416)

uruguay_unfactor <- read_dta("data/merged_uruguay_2007_2014.zip")

venezuela_unfactor <- read_dta("data/merged_venezuela_2007_2014.zip")
```



# Reading in 2016/17 files
Because there is no pre-existing merge that include 2016/17 data, we are reading it in separately and then joining it later in the process.

If you are using the new merged files, you can skip this.



## Creating unfactored dataframes of 2016/17 questionnaires using `read_dta`
This is the unfactored version of the 16/17 data frames, but we needed to apply modifications for when we eventually combined the 16/17 with the merged. 
We renamed the unique ID column to `person_id` and transformed it to a character. This does not affect the data, but is necessary for the join.
```{r Create unfactored df(16)}
argentina_16_unfactor <- read_dta("data/2016_argentina.dta") %>%
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

bolivia_16_unfactor  <- read_dta("data/2016_bolivia.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

brazil_16_unfactor  <- read_dta("data/2016_brazil.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

canada_16_unfactor  <- read_dta("data/2016_canada.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

chile_16_unfactor  <- read_dta("data/2016_chile.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

colombia_16_unfactor  <- read_dta("data/2016_chile.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

costa_16_unfactor  <- read_dta("data/2016_costa_rica.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

ecuador_16_unfactor  <- read_dta("data/2016_ecuador.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

elsalvador_16_unfactor  <- read_dta("data/2016_el_salvador.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

guatemala_16_unfactor  <- read_dta("data/2016_guatemala.dta") %>%
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

guyana_16_unfactor  <- read_dta("data/2016_guyana.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

honduras_16_unfactor  <- read_dta("data/2016_honduras.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

jamaica_16_unfactor  <- read_dta("data/2016_jamaica.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

mexico_16_unfactor  <- read_dta("data/2016_mexico.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

nicaragua_16_unfactor  <- read_dta("data/2016_nicaragua.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

panama_16_unfactor  <- read_dta("data/2016_panama.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

paraguay_16_unfactor <- read_dta("data/2016_paraguay.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

peru_16_unfactor  <- read_dta("data/2016_peru.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

usa_16_unfactor  <- read_dta("data/2016_united_states.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

uruguay_16_unfactor  <- read_dta("data/2016_uruguay.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))

venezuela_16_unfactor  <- read_dta("data/2016_venezuela.dta") %>% 
  rename(person_id = uniq_id) %>% 
  assert(is_uniq, person_id) %>% 
  transform(person_id = as.character(person_id))
```



