---
title: "lengthening & recoding"
output: html_notebook
---

# lengthening

this part transform the data from wide to long
the output long data has six columns: person_id, pais, country, weight, column_name, answer_measure

```{r}
question_list <- colnames(all.df)
remove <- c('pais','person_id','weight1500','country','X1')
question_list <- question_list[!question_list %in% remove]
final_data_long <- all.df %>% 
  # group_by(person_id,country) %>% # >> hack added to make person_id unique
  # mutate(rowid = row_number()) %>%
  # ungroup() %>%
  # mutate(person_id = paste(person_id, rowid, sep="_")) %>%
  # select(-rowid) %>%# << hack added to make person_id unique
  gather(column_name, answer_measure, question_list) %>% 
  select(person_id,pais,country,column_name,answer_measure,weight1500)
```

# Understand what is going on with strange values
```{r}
# library(stringr)
# problematic <- filter(final_data_long, answer_measure%in%c(98,99,100)&column_name!="q2")
# table(problematic$column_name,problematic$answer_measure)
# table(problematic$column_name,str_match(problematic$person_id,".{3}(\\d{2})")[,2])
# table(problematic$column_name,problematic$country)
# table(problematic$answer_measure)
# problematic %>% filter(answer_measure==100)
```

# recoding

this part will recode the answer_measure column to a sacle of 0-100
if there is no value recoded, the answer measure will show its original answer


## Then, the actual recoding

```{r}
total_long_common_recoded <- final_data_long %>%
  mutate(answer_measure = as.character(answer_measure)) %>%
  left_join(response_labels, 
            by = c("column_name" = "column_name", "answer_measure" = "value")) %>%
  mutate(answer_dimension = if_else(column_name=="year"|is.na(label), #make sure year is ok for dropdown menu
                                    label,
                                    paste0(answer_measure, ": ", label)),
         answer_measure = if_else(is.na(value_recoded),answer_measure,value_recoded)
         )
  # hack to get better labels on crosstab
  # group_by(column_name) %>%
  # mutate(sortid=as.integer(as.factor(answer_measure))) %>%
  # mutate(sortid=max(sortid,na.rm = T)-sortid) %>%
  # ungroup() %>%
  # mutate(answer_dimension = if_else(is.na(label_es),
  #                                   label_es,
  #                                   str_c('"',str_dup(" ",sortid), label_es,'"')),
  #        sortid = NULL)
```
# add age group

this part will add age group as a dimension

```{r}
# Separate our q2 rows, add agegroup, then bind all together
common_only_q2 <-
  total_long_common_recoded %>% filter(column_name == "q2") %>%
  mutate(answer_dimension = as.character(cut(
    as.numeric(answer_measure),
    breaks = c(0, 25, 35, 45, 55, 65, Inf),
    labels = c("18-25", "26-35", "36-45", "46-55", "56-65", "66-")
  )))

# stacking back into full data
total_long_common_recoded <- total_long_common_recoded %>% 
  filter(column_name !="q2") %>%  #Only non-q2 rows left
  bind_rows(common_only_q2)
```


# assert

check the age group
it should show actual age in measure and age group in dimension

```{r age_group}
total_long_common_recoded %>% 
  filter(column_name == 'q2') %>% 
  select(answer_measure,answer_dimension)
```

check the year recoding
2009 is recoded to 2008
2017 is recoded to 2016
2019 is recoded to 2018

```{r}
total_long_common_recoded %>% 
  filter(column_name == 'year') %>% 
  distinct(answer_measure)
```



## Combining category and question

```{r Combine category and question}
total_long_common_narrow <- total_long_common_recoded %>% 
  left_join(questions_cats, by = "column_name") %>%
  rename(category_short = paste0("category_short_",lang), question_short = paste0("question_short_",lang)) %>% 
  unite(category_question, category_short, question_short, sep = ":", remove = FALSE) %>%
  unite(category_colname, category_short, column_name, sep = ":", remove = FALSE) %>%
  select(country, person_id, weight1500, column_name, category_question, category_colname, question_short, column_name, answer_measure, answer_dimension) 
```

## Pivoting Wider 

This part will transform the data from long to wide for tableau

Explicitly name the dimensions and measures 

Define list of all columns names that are measures
```{r Create measures/dimensions list}
measures <- c(
      "a4",
      "aoj11",
      "aoj12",
      "b1",
      "b12",
      "b13",
      "b18",
      "b2",
      "b20",
      "b20a",
      "b21",
      "b21a",
      "b3",
      "b31",
      "b32",
      "b37",
      "b4",
      "b47a",
      "b6",
      "cct1b",
      "clien1n",
      "clien1na",
      "cp13",
      "cp2",
      "cp20",
      "cp6",
      "cp7",
      "cp8",
      "d1",
      "d2",
      "d3",
      "d4",
      "d5",
      "d6",
      "drk1",
      "dst1b",
      "e5",
      "ed",
      "eff1",
      "eff2",
      "env1c",
      "env2b",
      "etid",
      "exc11",
      "exc13",
      "exc14",
      "exc15",
      "exc16",
      "exc18",
      "exc2",
      "exc20",
      "exc6",
      "exc7",
      "exc7new",
      "fs2",
      "fs8",
      "gi0",
      "gi0n",
      "idio2",
      "infrax",
      "ing4",
      "it1",
      "jc10",
      "jc13",
      "jc15a",
      "jc16a",
      "l1",
      "l1b",
      "leng1",
      "lib1",
      "lib2c",
      "m1",
      "mil10a",
      "mil10e",
      "np1",
      "ocup1a",
      "ocup4a",
      "pn4",
      "pol1",
      "prot3",
      "q1",
      "q10a",
      "q10e",
      "q10new",
      "q11n",
      "q12",
      "q12bn",
      "q12c",
      "q14",
      "q2",
      "q3cn",
      "q5a",
      "q5b",
      "r1",
      "r12",
      "r14",
      "r15",
      "r16",
      "r18",
      "r3",
      "r4",
      "r4a",
      "r5",
      "r6",
      "r7",
      "r8",
      "redist1",
      "redist2",
      "redist2a",
      "redist3",
      "ros4",
      "sd2new2",
      "sd3new2",
      "sd6new2",
      "smedia1",
      "smedia4",
      "smedia7",
      "soct2",
      "vb10",
      "vb2",
      "vb20",
      "vb50",
      "vb51",
      "vb52",
      "vic1ext",
      "vic1exta",
      "w14a",
      "wf1"
    )

dimensions <- c(
      "a4",
      "aoj11",
      "aoj12",
      "b1",
      "b12",
      "b13",
      "b18",
      "b2",
      "b20",
      "b20a",
      "b21",
      "b21a",
      "b3",
      "b31",
      "b32",
      "b37",
      "b4",
      "b47a",
      "b6",
      "cct1b",
      "clien1n",
      "clien1na",
      "cp13",
      "cp2",
      "cp20",
      "cp6",
      "cp7",
      "cp8",
      "d1",
      "d2",
      "d3",
      "d4",
      "d5",
      "d6",
      "drk1",
      "dst1b",
      "e5",
      "ed",
      "eff1",
      "eff2",
      "env1c",
      "env2b",
      "etid",
      "exc11",
      "exc13",
      "exc14",
      "exc15",
      "exc16",
      "exc18",
      "exc2",
      "exc20",
      "exc6",
      "exc7",
      "exc7new",
      "fs2",
      "fs8",
      "gi0",
      "gi0n",
      "idio2",
      "infrax",
      "ing4",
      "it1",
      "jc10",
      "jc13",
      "jc15a",
      "jc16a",
      "l1",
      "l1b",
      "leng1",
      "lib1",
      "lib2c",
      "m1",
      "mil10a",
      "mil10e",
      "np1",
      "ocup1a",
      "ocup4a",
      "pn4",
      "pol1",
      "prot3",
      "q1",
      "q10a",
      "q10e",
      "q10new",
      "q11n",
      "q12",
      "q12bn",
      "q12c",
      "q14",
      "q2",
      "q3cn",
      "q5a",
      "q5b",
      "r1",
      "r12",
      "r14",
      "r15",
      "r16",
      "r18",
      "r3",
      "r4",
      "r4a",
      "r5",
      "r6",
      "r7",
      "r8",
      "redist1",
      "redist2",
      "redist2a",
      "redist3",
      "ros4",
      "sd2new2",
      "sd3new2",
      "sd6new2",
      "smedia1",
      "smedia4",
      "smedia7",
      "soct2",
      "ur",
      "vb10",
      "vb2",
      "vb20",
      "vb50",
      "vb51",
      "vb52",
      "vic1ext",
      "vic1exta",
      "w14a",
      "wf1",
      "year"
    )
```


```{r Save wide data as .csv}
final_wide_measure <-
  total_long_common_narrow %>% # Include only measures (cols with recode)
  filter(
    column_name %in% measures
  ) %>%
  pivot_wider(
    id_cols = c(person_id, country,weight1500),
    names_from = column_name,
    values_from = answer_measure
  )
# Put _m or m_ in names here to simplify measure/dimension designation

final_wide_dimension <-
  total_long_common_narrow %>% # Include only dimensions (cols with label or no recode )
  filter(
    column_name %in% dimensions
  ) %>%
  pivot_wider(
    id_cols = c(person_id, country,weight1500),
    names_from = column_name,
    values_from = answer_dimension
  )

final_wide <- final_wide_dimension %>%
  left_join(final_wide_measure, by = c("person_id", "country",'weight1500'), suffix = c("_d", "_m"))
  
  
#join

# Update the version of the csv to reflect code cleanup
#Updating to version 6 to reflect the work on updating the lookup tables


write_csv(final_wide, "lapop_wide_en_v1.csv", na = "NULL ") 

```



Checks that were previously earlier:
check if the recoding value is in sacle of 0-100

```{r}
distinct(final_wide,a4)
```



```{r}
distinct(final_wide,b13)
distinct(final_wide,jc13)
distinct(final_wide,exc16)
distinct(final_wide,exc11)

```

```{r}
all.df %>% 
  filter(country == 'Colombia') %>% 
  distinct(b4)
```
```{r}
final_wide %>% filter(a4_m == 62)
```
