---
title: "3-gen-selector-code"
output:
  html_document:
    df_print: paged
    toc: true
---

# Generate Selector Code for Tableau

See https://help.tableau.com/current/pro/desktop/en-us/changing-views-using-parameters.htm for background on where to put this generated code.

Use dimensions and measures lists. 

Join to lookup tables to get short categories and short questions

Use Glue to put together string or prints

<!-- yes  -->

```{r, echo=F, results = 'hide'}
# remove leading ## from html output
library(knitr)
opts_chunk$set(comment="")
```


## Create category/short question dataframe
```{r setup, echo=FALSE, results='hide'}
 library(glue)

cat_numxl <- read_csv("lookups/questions_categories_v1-2.csv") 

measures_cat_short <- tibble(column_name = measures) %>%
  left_join(cat_numxl, by=("column_name")) %>%
  select(column_name, paste0("category_short_",lang), paste0("question_short_",lang), paste0("question_",lang)) %>%
  rename(category_short = paste0("category_short_",lang), question_short = paste0("question_short_",lang), question = paste0("question_",lang)) %>% 
  semi_join(total_long_common_narrow, by = "column_name") #Remove any column_names that are not in total_long_common_narrow

dimensions_cat_short <- tibble(column_name = dimensions) %>%
  left_join(cat_numxl, by=("column_name")) %>%
  select(column_name, paste0("category_short_",lang), paste0("question_short_",lang), paste0("question_",lang)) %>% 
  rename(category_short = paste0("category_short_",lang), question_short = paste0("question_short_",lang), question = paste0("question_",lang)) %>%
  semi_join(total_long_common_narrow, by = "column_name") #Remove any column_names that are not in total_long_common_narrow

```


## Parameter definition


Copy and paste this output into the Parameter dialog to select variables and set text for them
```{r var selection, echo=FALSE, comment=""}
measures_cat_short %>% 
  arrange(paste0(category_short, question_short)) %>% 
  glue_data('{column_name}, {category_short}:{question_short} ({column_name})' )
```


## Calculated measure field code for Calculated Field

In Tableau, custom parameters will be used to select variables to display on the dashboards. The following output should be cut and pasted into the code window for calculated fields. 

Code to calculate field "*Variable*"
```{r define measure variable, echo=FALSE}
cat("CASE [Choose Variable]
")

measures_cat_short %>% 
  glue_data(paste0("WHEN '{column_name}' THEN [{column_name}","_m","]"))

cat("ELSE NULL
END")
```

Code to calculate field "*Variable Label*"
```{r define measure label, echo=FALSE}
cat("CASE [Choose Variable]
")

measures_cat_short %>% 
  glue_data(paste0("WHEN '{column_name}' THEN [{column_name}","_l","]"))

cat("ELSE NULL
END")
```



## Calculated Field Code for Question Text Short

Cut and paste the code below into a field for Short Question (I think we're currently not using, but maybe we want to?)

```{r define question text to display, echo=FALSE}
cat("CASE [Choose Variable]
")

measures_cat_short %>% 
  glue_data("WHEN '{column_name}' THEN '{question_short}'")

cat("ELSE ''
END")
```


## Calculated Field Code for Question Text Long

Cut and paste the code below into a calculated field for *Full Question*

```{r define long question text to display, echo=FALSE}
cat("CASE [Choose Variable]
")

measures_cat_short %>% 
  glue_data("WHEN '{column_name}' THEN '{question}'")

cat("ELSE ''
END")
```

## Code for Calculated Field Anchor Text

For numerics with both numbers and text, just the text.

## Code for Dimensions Parameter

Copy and paste this output into the Parameter dialog to select dimension variables and set text for them

```{r select dimension, echo=FALSE}
dimensions_cat_short %>% 
  arrange(category_short, question_short) %>% 
  glue_data('{column_name}, {category_short}:{question_short} ({column_name})')
```

## Code for Dimensions Text


## Calculated Dimension field code for Calculated Field

In Tableau, custom parameters will be used to select variables to display on the dashboards. The following output should be cut and pasted into the code window for calculated fields. 

Code to calculate field "*Dimension*"
```{r define dimension variable, echo=FALSE}
cat("CASE [Choose Crosstab Dimension]
")

dimensions_cat_short %>% 
  glue_data(paste0("WHEN '{column_name}' THEN [{column_name}","_d","]"))

cat("ELSE NULL
END")
```

Code to calculate field "*Dimension Order*"
```{r define dimension sort order, echo=FALSE}
cat("CASE [Choose Crosstab Dimension]
")

dimensions_cat_short %>% 
  glue_data(paste0("WHEN '{column_name}' THEN [{column_name}","_o","]"))

cat("ELSE NULL
END")
```

## Generate code for Calculated Field for measure label/values

Grouped mutate to roll up multiple lines into one with /n separators, tabs?

```{r val label setup, echo=FALSE, results='hide'}
label_val <- read_csv("lookups/values_labels_v1-3.csv",col_types = cols(.default = col_character()), na = "NA") %>%
  rename(label = paste0("label_",lang)) %>%
  mutate(value_recoded = if_else(is.na(value_recoded), value, value_recoded))

```

Code to calculate field "*Label Value*"
```{r calc measure, echo=FALSE}
  cat("CASE [Choose Variable]
")

label_val %>% 
  group_by(column_name) %>% 
  distinct(label, .keep_all = T) %>%
  summarise(lab_val = paste0(label, "--", value_recoded, collapse = "\n")) %>% 
  ungroup() %>%
  glue_data("WHEN '{column_name}' THEN '{lab_val}'")

cat("ELSE NULL
END")
  
# rmarkdown::render("C:/Users/plutowl/Documents/GitHub/lapop-dashboard/3-gen-selector-code.Rmd")
```

