---
title: "3-Adding Wave Column"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure
The 2016 and 2017 files are missing the year and wave columns that are present in the merged files. The code below adds the correct wave to the corresponding files. There are then functions written for the factored and unfactored versions that add a wave column with the appropriate year.

Note: we use wave instead of year because in some instances the questionnaire is conducted in January of the following year, but is still a part of the previous wave. (e.g. interview is conducted Jan 1, 2005 but wave is 2004)

And as a reminder, you have to do *both* the factored and unfactored versions.

This step is only required for when individual years need to be combined with a larger merge. Merged datasets should have the wave column.

If your individual years differ from 16/17, you will need to change the name of the datasets and use the correct year in the add wave function.

## Lists of files by year
```{r Create df list}
countries_2016 <-
  list(
    argentina_16_unfactor,
    bolivia_16_unfactor,
    brazil_16_unfactor,
    canada_16_unfactor,
    chile_16_unfactor,
    guatemala_16_unfactor,
    jamaica_16_unfactor,
    mexico_16_unfactor,
    peru_16_unfactor,
    usa_16_unfactor,
    uruguay_16_unfactor,
    colombia_16_unfactor,
    costa_16_unfactor,
    elsalvador_16_unfactor,
    guyana_16_unfactor,
    honduras_16_unfactor,
    nicaragua_16_unfactor,
    paraguay_16_unfactor,
    ecuador_16_unfactor,
    venezuela_16_unfactor
  )
```

## Function to adding wave column
### For unfactored datasets
```{r Define add_wave_unfactor_2016()}
add_wave_unfactor_2016 <- function(country){
  #Adds new column, wave, with appropriate year
  country <- country %>%
    mutate(wave = 2016)
  return(country)
}
```

# 2016/17 datasets, factored and unfactored
```{r Add wave into 16/17 df}
#Argentina
argentina_16_unfactor <- add_wave_unfactor_2016(argentina_16_unfactor)

#Bolivia
bolivia_16_unfactor <- add_wave_unfactor_2016(bolivia_16_unfactor)

#Brazil
brazil_16_unfactor <- add_wave_unfactor_2016(brazil_16_unfactor)

#Canada
canada_16_unfactor <- add_wave_unfactor_2016(canada_16_unfactor)

#Chile
chile_16_unfactor <- add_wave_unfactor_2016(chile_16_unfactor)

#Colombia
colombia_16_unfactor <- add_wave_unfactor_2016(colombia_16_unfactor)

#Costa Rica
costa_16_unfactor <- add_wave_unfactor_2016(costa_16_unfactor)

#Ecuador
ecuador_16_unfactor <- add_wave_unfactor_2016(ecuador_16_unfactor)

#El Salvador
elsalvador_16_unfactor <- add_wave_unfactor_2016(elsalvador_16_unfactor)

#Guatemala
guatemala_16_unfactor <- add_wave_unfactor_2016(guatemala_16_unfactor) 

#Guyana
guyana_16_unfactor <- add_wave_unfactor_2016(guyana_16_unfactor)

#Honduras
honduras_16_unfactor <- add_wave_unfactor_2016(honduras_16_unfactor)

#Jamaica
jamaica_16_unfactor <- add_wave_unfactor_2016(jamaica_16_unfactor)

#Mexico
mexico_16_unfactor <- add_wave_unfactor_2016(mexico_16_unfactor)

#Nicaragua
nicaragua_16_unfactor <- add_wave_unfactor_2016(nicaragua_16_unfactor)

#Panama
panama_16_unfactor <- add_wave_unfactor_2016(panama_16_unfactor)

#Paraguay
paraguay_16_unfactor <- add_wave_unfactor_2016(paraguay_16_unfactor)

#Peru
peru_16_unfactor <- add_wave_unfactor_2016(peru_16_unfactor)

#United States
usa_16_unfactor <- add_wave_unfactor_2016(usa_16_unfactor)

#Uruguay
uruguay_16_unfactor <- add_wave_unfactor_2016(uruguay_16_unfactor)

#Venezuela
venezuela_16_unfactor <- add_wave_unfactor_2016(venezuela_16_unfactor)
```