---
title: "4-Creating Unique ID"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure
This section makes a unique ID for all merged country dataframes. The 2016/17 files already contain a unique identifier, and we used this as the template for making the unique ID in the merged files.

First, there is a function written for the unfactored countries that is then applied to all unfactored merged countries.

Then, a similar function is written for the factored countries, but in this step we add "_factor" to the end of each column name to signifiy that it belongs to the factored dataset.

The unfactored and factored datasets will be joined later in the process.

## Function to make unique ID for unfactored countries
```{r}
making_uniqueID <- function(country){
  #Combines idnum and idnum_14 with "/"
  country <- mutate(country,
                    idnum = ifelse(idnum_14 == '',
                                   idnum,
                                   paste(idnum,idnum_14,sep = "_"))) %>%
    mutate(., idnum = paste(idnum, row_number(), sep = "_")) %>% 
    #Makes new column, person_id
    mutate(.,
           person_id = paste(
             paste(
               #Takes first 3 letters of country names and capitalizes it
               toupper(substr(pais, 1, 3)),
               #Selects last two digits of year
               substr(year, 3, 4), sep = ''),
             #Separates the country name from the year with underscore
             idnum, sep = "_"))
  
  #Converts person_id column to a character
  country <- transform(country, person_id = as.character(person_id)) %>% 
    assert(is_uniq, person_id)
  return(country)
}
```

#### Applying `making_uniqueID` to all unfactored, merged countries
Note: Guayana and Jamaica are written in English only. This will affect the way the tableau looks, so if you do not want them in your visualizations, you can comment them out by adding a hashtag # before it. 
```{r}
argentina_unique_unfactor <- making_uniqueID(argentina_unfactor)
belize_unique_unfactor <- making_uniqueID(belize_unfactor)
bolivia_unique_unfactor <- making_uniqueID(bolivia_unfactor)
brazil_unique_unfactor <- making_uniqueID(brazil_unfactor)
canada_unique_unfactor <- making_uniqueID(canada_unfactor)
chile_unique_unfactor <- making_uniqueID(chile_unfactor)
colombia_unique_unfactor <- making_uniqueID(colombia_unfactor)
costa_unique_unfactor <- making_uniqueID(costa_unfactor)
ecuador_unique_unfactor <- making_uniqueID(ecuador_unfactor)
elsalvador_unique_unfactor <- making_uniqueID(elsalvador_unfactor)
guatemala_unique_unfactor <- making_uniqueID(guatemala_unfactor)
guyana_unique_unfactor <- making_uniqueID(guyana_unfactor)
honduras_unique_unfactor <- making_uniqueID(honduras_unfactor)
jamaica_unique_unfactor <- making_uniqueID(jamaica_unfactor)
mexico_unique_unfactor <- making_uniqueID(mexico_unfactor)
nicaragua_unique_unfactor <- making_uniqueID(nicaragua_unfactor)
panama_unique_unfactor <- making_uniqueID(panama_unfactor)
paraguay_unique_unfactor <- making_uniqueID(paraguay_unfactor)
peru_unique_unfactor <- making_uniqueID(peru_unfactor)
suriname_unique_unfactor <- making_uniqueID(suriname_unfactor)
usa_unique_unfactor <- making_uniqueID(usa_unfactor)
uruguay_unique_unfactor <- making_uniqueID(uruguay_unfactor)
venezuela_unique_unfactor <- making_uniqueID(venezuela_unfactor)
```

## Function to make unique ID for factored countries
The function below is the same as above, except `making_uniqueID` is now `making_uniqueID_factor` to indicate it needs to be used for factored data
```{r}
making_uniqueID_factor <- function(country){
  #Combines idnum and idnum_14 with "/" and then makes unique id
  country <- mutate(country,
                    idnum_factor = ifelse(idnum_14_factor == '',
                                   idnum_factor,
                                   paste(idnum_factor,idnum_14_factor, sep = "_"))) %>%
    mutate(., idnum_factor = paste(idnum_factor, row_number(), sep = "_")) %>% 
    #Makes new column, uniq_id_factor
    mutate(.,
           person_id_factor = paste(
             paste(
               #Takes first 3 letters of country names and capitalizes it
               toupper(substr(pais_factor, 1, 3)),
               #Selects last two digits of year
               substr(year_factor, 3, 4), sep = ''),
             #Separates the country name from the year with underscore
             idnum_factor, sep = "_"))
  #Converts uniq_id column to a character
  country <- transform(country, person_id_factor = as.character(person_id_factor)) %>% 
    assert(is_uniq, person_id_factor)
  return(country)
}
```


#### Applying `making_uniqueID_factor` to all countries
The note about Guyana and Jamiaca apply here as well.
```{r}
argentina_unique_factor <- making_uniqueID_factor(argentina_factor)
belize_unique_factor <- making_uniqueID_factor(belize_factor)
bolivia_unique_factor <- making_uniqueID_factor(bolivia_factor)
brazil_unique_factor <- making_uniqueID_factor(brazil_factor)
canada_unique_factor <- making_uniqueID_factor(canada_factor)
chile_unique_factor <- making_uniqueID_factor(chile_factor)
colombia_unique_factor <- making_uniqueID_factor(colombia_factor)
costa_unique_factor <- making_uniqueID_factor(costa_factor)
ecuador_unique_factor <- making_uniqueID_factor(ecuador_factor)
elsalvador_unique_factor <- making_uniqueID_factor(elsalvador_factor)
guatemala_unique_factor <- making_uniqueID_factor(guatemala_factor)
guyana_unique_factor <- making_uniqueID_factor(guyana_factor)
honduras_unique_factor <- making_uniqueID_factor(honduras_factor)
jamaica_unique_factor <- making_uniqueID_factor(jamaica_factor)
mexico_unique_factor <- making_uniqueID_factor(mexico_factor)
nicaragua_unique_factor <- making_uniqueID_factor(nicaragua_factor)
panama_unique_factor <- making_uniqueID_factor(panama_factor)
paraguay_unique_factor <- making_uniqueID_factor(paraguay_factor)
peru_unique_factor <- making_uniqueID_factor(peru_factor)
suriname_unique_factor <- making_uniqueID_factor(suriname_factor)
usa_unique_factor <- making_uniqueID_factor(usa_factor)
uruguay_unique_factor <- making_uniqueID_factor(uruguay_factor)
venezuela_unique_factor <- making_uniqueID_factor(venezuela_factor)
```