---
title: "Finding Common Questions"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure
In order to cut down on the size of the data, we are reducing the total combination of all countries to the common questions.

```{r Import libraries, message=FALSE}
library(janitor)
library(rlang)
```


## NOTE: SEE ISSUE #35

LAPOP has defined which questions to inlcude. Rather than determining which questions appear across all country questionnaires, we'll do a lookup using 

QWORD_2018_Core_10plus_countries(v1.0).csv
LAB_VAL_2018_Core_10plus_countries(v1.0).csv

QWORD_2018_Core_10plus_countries(v1.0).csv
LAB_VAL_2018_Core_10plus_countries(v1.0).csv

contain a listing of all of the questions (QWORD) and values (LAB_VAL) for all survey questions that appeared in 10 or more countries in the 2018 wave. 

We will use this data to:
1. Define the common questions that are to appear in the dashboards (Issue #37)
2. Rescale the values for each of the responses to be between 0 and 100 (Issue #32)
3. Group by age group (Issue #29)

We will read in the data here, and address 1-3 elsewhere in the code (follow the commits closing each issue to identify where these tables are used)

## Read in reference tables

```{r Read in question label value}
label_val <-
  read_csv(
    "LAB_VAL_2018_Core_10plus_countries(v1.0).csv",
    col_types = cols(recoded = col_character(),
                     value = col_character()),
    locale = locale(encoding = "ISO-8859-1")
  ) %>%
  clean_names()
qword <- read_csv("QWORD_2018_Core_10plus_countries(v1.0).csv", 
    locale = locale(encoding = "ISO-8859-1")) %>%
  clean_names()
```

Using the lookup tables above, filter out the questions that are not in the list

Use qword, then get unique of question, feed to find_common.



```{r Find common questions}
#Common questions as defined by LAPOP 
common_questions <- qword %>%
  select(column_name = name, question = qword_esp) %>%
  distinct()

#Creating a list with all the clean data frames
countries <- list(argentina_clean, belize_clean, bolivia_clean, brazil_clean, canada_clean, chile_clean, costa_clean, ecuador_clean, elsalvador_clean, guatemala_clean, guyana_clean, honduras_clean, jamaica_clean, mexico_clean, nicaragua_clean, panama_clean, paraguay_clean, peru_clean, suriname_clean, uruguay_clean, usa_clean, venezuela_clean) #colombia_clean not resolved

#Function for joining dataframes to ensure each country has only the common questions
find_common <- function(country_dfr, questions_dfr) {
  semi_join(country_dfr, questions_dfr, by = "column_name")
}

#Applying `map_dfr` to create combined dataframe
#countries_common_only <- map_dfr(countries, find_common, common_questions)

#Trying `map_dfr` on combined_clean
total_long_common <- find_common(combined_clean, common_questions) 

```

*NOTE*

There are 96 questions that came across. See which ones were dropped from list. Issue

Testing
```{r}
argentina_clean %>%
  semi_join(common_questions, by = "column_name") %>%
  tabyl(question)
```
