---
title: "90-output-tests"
output: html_notebook
---

```{r}
library(daff)
library(readr)
```

# Check Differences Between CSV Output versions

We are refactoring a significant portion of the code base and need to ensure that changes to the final produce data tables change in an understandable way. 

Version 4 lapop_wide_v4.csv is the last version written by the old code base. New versions need to write a file that is the same structure and fundamentally the same data as that one. 

## Compare Version 4 and Version 4

### Read Versions 4 and 5
```{r}
# not needed
lwv4 <- read_csv("lapop_wide_v4.csv", na = "NULL ") 
lwv5 <- read_csv("lapop_wide_v5.csv", na = "NULL ") 
```

## Compare Data Frames Function
```{r}
comp_df <- function (org_df, new_df) {
  org_df <- read_csv(org_df, na = "NULL ") 
  new_df <- read_csv(new_df, na = "NULL ") 
  render_diff(
    diff_data(data_ref = org_df,
              data = new_df)
  )
}
```

comp_df will return number of differences and the instances of differences in;
1) rows
2) columns
3) and cells

## Compare Data Frames
```{r}
comp_df("lapop_wide_v4.csv","lapop_wide_v5.csv")
```
